The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-01-30 Text/paper.tex
Added some stuff in paper.text

\documentclass[a4paper,12pt]{article}

@@

\begin{document}
\maketitle
\titlepage

\tableofcontents
\clearpage

@@

\section{Introduction}
Introduction

@@

\subsection{Intelligent Systems Schnapsen Framework}
The course provided us with a framework. We have an api, which is the skeleton for the Schnapsen game, and we have two scripts: one where we can let bots play against each other in a single game where we can see all the moves, and a script where we can play a tournament - with a specifiable number of the number of games to be played - and see how many games each bot has won. There are already multiple bots already present in the framework to play against:
\begin{description}
\item [Minimax / Alphabeta:] This bot only works in a perfect-information game (phase 2 of Schnapsen). It recursively looks through all the states, and decides what the best move to play will be, provided that the opponent plays optimally, and will try to minimize the outcome of the game for the player.
\item [Bully:] Plays by a defined set of rules. If it has a trump card, it will play that. Otherwise, it will play a card of the same suit player 1 played. If it cannot do either of those things, it will play the highest ranking card of any suit.
\item [Rand:] Chooses a random move out of all of the legal moves, and plays that.
\item [Rdeep:] Functions quite like a Monte-Carlo sampling bot. It looks through multiple states, and averages the heuristics of a state, thereby ranking the moves. It then picks one of the highest ranking moves to play.
\item [KBbot:] Logical reasoning bot. The strategy can be defined in propositional logic. The current strategy of the bot is to always play cheap cards (i.e kings, queens, jacks) first.
\end{description}

@@

\section{Research Question}

\section{Experimental setup}

@@

>>>>

\documentclass[a4paper,11pt]{article}

@@

\begin{document}
\maketitle
\clearpage

@@

\section{Introduction}
Artificial Intelligence is becoming a huge subject, and we see it appearing more and more in daily life: voice assistants on smartphones, self-driving Tesla's, AlphaGo defeating Go masters, and so on. ... We can make a distinction between strong and weak AI [1]: \textit{weak AI} is focused on mastering problems in one limited area, whereas \textit{strong AI} is considered to be Artificial Intelligence with \textit{actual} intelligence, and even self-awareness. For this paper, we will be focussing on weak AI in games, more specifically in the game of Schnapsen. In section 2 we will describe Schnapsen in more detail, alongside the bots used for the game. The research question will be described in section 3. In section 4, we will talk more about the experiment. ...

@@

\subsection{Intelligent Systems Schnapsen Framework}
An API in Python has been provided, together with a framework for the Schnapsen game. Furthermore, we  have two scripts: one where bots can play against each other in a single game where all moves in the game can be seen, and a script where bots can play a tournament against each other - with a specifiable number of the number of games to be played - and where the number of won games per robot can be seen. There are already multiple bots already present in the framework to play against:
\begin{description}
\item [Minimax / Alphabeta:] This bot only works in a perfect-information game (phase 2 of Schnapsen). It recursively looks through all the states, and decides what the best move to play will be, provided that the opponent plays optimally, and will try to minimize the outcome of the game for the player.
\item [Bully:] Plays by a defined set of rules. If it has a trump card, it will play that. Otherwise, it will play a card of the same suit player 1 played. If it cannot do either of those things, it will play the highest ranking card of any suit.
\item [Rand:] Chooses a random move out of all of the legal moves, and plays that.
\item [Rdeep:] Functions quite like a Monte-Carlo sampling bot. It looks through multiple states, and averages the heuristics of a state, thereby ranking the moves. It then picks one of the highest ranking moves to play.
\item [KBbot:] Logical reasoning bot. The strategy can be defined in propositional logic. The current strategy of the bot is to always play cheap cards (i.e kings, queens, jacks) first.
\end{description}

@@

\section{Research Question}
In our research, we want to find out if an extended feature space in a machine learning bot will improve its performance in Schnapsen. There is already a machine learning bot present, with what we will call, the \textit{default feature space}, provided by the framework. Our goal is to extend and improve this feature space, and see if the bot will have a better performance. Our hypothesis is that an extended feature space will lead to a better performance, since ..... \\ \\
\noindent
The \textit{default feature space} contains the following features:
\begin{itemize}
\item Perspective information
\item Player 1's point count
\item Player 2's point count
\item Player 1's pending points
\item Player 2's pending points
\item The trump suit
\item The phase
\item The stock size
\item The leader
\item Whose turn it is currently
\item The played card of the opponenet
\end{itemize}

\section{Experimental setup}
For the testing of the bots, multiple Schnapsen tournaments were held. Each bot played a 100 games against every other bot. The competing bots were:
\begin{itemize}
\item Minimax
\item Bully
\item Rand
\item Rdeep
\item KBBot
\item ML
\item MLAdvanced
\end{itemize}

Both ML, and MLAdvanced were trained on the same bot. First, bully, then rand, then rdeep, then kbbot, etc.

@@

\section{References}
1. http://humanparagon.com/strong-and-weak-ai/
